---
title: "P8105_hw6_qy2234"
author: "Michael Yan"
date: "11/21/2019"
output: github_document
---

```{r}
#### general setup
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
library(patchwork)
library(rvest)
library(modelr)
library(mgcv)
devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# problem 1
```{r}
#### load and clean the birthweight data
birthweight_data = read_csv("./data/birthweight.csv") %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))

#### check for missing data in all columns
birthweight_data %>% 
  summarise_all(funs(sum(is.na(.)))) %>% 
  knitr::kable()
```

```{r}
#### create a stepwise regression
fit_test = lm(bwt ~ ., data = birthweight_data)
step(fit_test, direction = 'backward')
```

* The results show that the model should include bwt ~ babysex + bhead + blength + delwt + fincome +  gaweeks + mheight + mrace + parity + ppwt + smoken. 

```{r}
#### test fitted regression model
fitted = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_data)
summary(fitted)
```

* Based on the results, we see that the adjusted R-squared is 0.7173 which is resonable and the overall p-value is less than 0.05, therefore the variables used above to predict birthweight are chosen to be our predictors.

```{r}
#### plot of model residuals against fitted values 
birthweight_data %>% 
  add_predictions(model = fitted, var = "prediction") %>% 
  add_residuals(model = fitted, var = "residuals") %>%
  ggplot(aes(x = prediction, y = residuals)) + 
  geom_point(alpha = 0.5, color = "blue") +
  geom_smooth(color = "red") + 
  labs(title = "residuals vs fitted values", 
       y = "Residuals",
       x = "Fitted Values")
```

* Based on the fitted line, which is suppose be around 0 residuals, we see that when the fitted value is low, outliers are present. In addition, outside the interval approximately from 2000-4000, the residuals are not normally distributed which is an indicator for unreliable model prediction.

```{r}
#### compare our model to two others
set.seed(1)

#### create training and testing dataset
crossv_mc(birthweight_data, 100) %>%
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
# fit each of three models to this dataset 
    mutate(fitted = map(train, ~lm(bwt ~ babysex + bhead + blength + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
           compare_model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
           compare_model_2 = map(train, ~lm(bwt ~ babysex + blength + bhead + babysex * blength + babysex * bhead + blength * bhead + babysex * blength * bhead, data = .x))) %>% 
    mutate(rmse_model_fitted = map2_dbl(fitted, test, ~rmse(model = .x, data = .y)),
           rmse_model_1 = map2_dbl(compare_model_1, test, ~rmse(model = .x, data = .y)),
           rmse_model_2 = map2_dbl(compare_model_2, test, ~rmse(model = .x, data = .y))) %>% 
    select(starts_with("rmse")) %>% 
    gather(key = model, value = rmse) %>% 
  
#### plot the prediction error distribution for different models  
    ggplot(aes(x = model, y = rmse, fill = model)) + 
    geom_boxplot(alpha = .5, color = " red") + 
    labs(title = "Compare Fitted Model To Two Others",
       x = "Models",
       y = "RMSE value")
```

* In general, we want a model that has the lowest RMSE value. In this case, our fitted model has the lowest RMSE among all three models which indicates that our model outperform the other two.


## Problem 2
```{r}
#### download weather dataset
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
#### simple linear regression with tmax as the response and tmin as the predictor
weather_slr = lm(tmax ~ tmin, data = weather_df)
summary(weather_slr)
```
$$\hat{Y} = 7.20850 + 1.03924X_i where Y = tmax and X = tmin$$
